Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-17 TABLE/magnifications.tex
finished the update to z=1.3457   * also ran spell-check

Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\

@@

CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies.\\

@@

Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\

>>>>

Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\

@@

CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\

@@

Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
